Hilbert space approximate Bayesian Gaussian processes using Stan

### 2020-03-25 Paper/manuscript_v2/manuscript_07_01.tex
Update affiliation

\date{ \small
$^1$ Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain. \break
$^2$ TODO\break
$^3$ Department of Computer Science, Aalto University, Finland\break
$^*$ Corresponding author, Email: gabriuma@gmail.com
}

>>>>

\date{ \small
$^1$ Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain. \break
$^2$ Department of Applied Mathematics and Computer Science, Technical University of Denmark, Denmark
$^3$ Department of Computer Science, Aalto University, Finland\break
$^*$ Corresponding author, Email: gabriuma@gmail.com
}
